### 2017-02-02 local-capability-machine.tex
Added lemmas about expression relation and so on

>>>>

\subsubsection{Observation relation}
\begin{lemma}[Observation relation ($\observations$) non-expansive]
  \label{lem:obs-rel-ne}
  \[
    W \nequal W' \Rightarrow \observations(W) \nequal \observations(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:obs-rel-ne}]
  % TODO
\end{proof}

\subsubsection{Register-file relation}
\begin{lemma}[Register-file relation ($\stdrr$) non-expansive]
  \label{lem:stdrr-ne}
  \[
    W \nequal W' \Rightarrow \stdrr(W) \nequal \stdrr(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:stdrr-ne}]
  % TODO
\end{proof}

\begin{lemma}[Register-file relation ($\stdrr$) monotone wrt $\futurewk$]
  \label{lem:stdrr-mono}
  \[
    W' \futurewk W \Rightarrow \stdrr(W') \nsupeq \stdrr(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:stdrr-mono}]
  % TODO
\end{proof}

\subsubsection{Expression relation}
\begin{lemma}[Expression relation ($\stder$) non-exapansive]
  \label{lem:stder-ne}
  \[
    W \nequal W' \Rightarrow \stder(W) \nequal \stder(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:stder-ne}]
